Exploring the structure of the bound proton with Deeply Virtual Compton Scattering

### 2019-05-10 eg6-letters/incoherent/incoherent_prl.tex
2 referee text changes

\date{\today}
\begin{abstract}
In the past two decades, deeply virtual Compton scattering of electrons has 
   been successfully used to advance our knowledge of the partonic structure of 
   the free proton and investigate correlations between the transverse position 
   and the longitudinal momentum of quarks inside the nucleon. Meanwhile, the 
   structure of bound nucleons in nuclei has only been studied in inclusive 
   deep-inelastic lepton scattering experiments off nuclear targets, showing a 
   significant difference in longitudinal momentum distribution of quarks 
   inside the bound nucleon, known as the EMC effect. In this work, we report the first beam spin asymmetry (BSA) 
   measurement of exclusive deeply virtual Compton scattering (DVCS) off a 
   proton bound in $^4$He.  The data used here were accumulated using a $6$ GeV 
   longitudinally polarized electron beam incident on
a pressurized $^4$He gaseous target placed within the CLAS spectrometer in Hall-B at the Thomas
Jefferson National Accelerator Facility. The azimuthal angle ($\phi$) dependence of the BSA was
studied in a wide range of virtual photon and scattered proton kinematics. The 
   $Q^2$, $x_B$,
and t dependencies of the BSA on the bound proton are compared with those on the free proton.
In the whole kinematical region of our measurements, the BSA on the bound proton is smaller by
20\% to 40\%, indicating possible medium modification of its partonic structure.
\end{abstract}
%\pacs{Valid PACS appear here}

@@

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. 
First, events were selected with $Q^2$ greater than $1$ GeV$^2$ and the 
$\gamma^*p$ invariant mass ($W=\sqrt{(q+p)^2}$, assuming that the initial 
nucleon is at rest) greater than $2$ GeV. This is a commonly accepted region of 
kinematics used by the previous DVCS experiments to ensure the applicability of 
the DVCS handbag diagram and avoid the nucleon resonance region. The squared 
transferred momentum to the recoil proton $t$, calculated from the 
four-momentum vectors of the incoming and outgoing photons, was required to be 
greater than a minimum kinematically allowed value ($t_{min}$) at given $Q^2$ 
and $W$ defined as: \begin{equation}
t_{min} 
   =-Q^{2}~\frac{2(1-~x_{B})(1~-~\sqrt{1~+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}},
\end{equation}
where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
proton mass. This cut was applied to avoid accepting events that appear in  
unphysical regions of kinematics due to detector resolution and radiative 
effects.  We specifically use the kinematics of the photons to determine $t$ 
because the initial proton kinematics is unknown due to Fermi motion.

>>>>

\date{\today}
\begin{abstract}
In the past two decades, deeply virtual Compton scattering of electrons has 
   been successfully used to advance our knowledge of the partonic structure of 
   the free proton and investigate correlations between the transverse position 
   and the longitudinal momentum of quarks inside the nucleon. Meanwhile, the 
   structure of bound nucleons in nuclei has been studied in inclusive 
   deep-inelastic lepton scattering experiments off nuclear targets, showing a 
   significant difference in longitudinal momentum distribution of quarks 
   inside the bound nucleon, known as the EMC effect. In this work, we report the first beam spin asymmetry (BSA) 
   measurement of exclusive deeply virtual Compton scattering (DVCS) off a 
   proton bound in $^4$He.  The data used here were accumulated using a $6$ GeV 
   longitudinally polarized electron beam incident on
a pressurized $^4$He gaseous target placed within the CLAS spectrometer in Hall-B at the Thomas
Jefferson National Accelerator Facility. The azimuthal angle ($\phi$) dependence of the BSA was
studied in a wide range of virtual photon and scattered proton kinematics. The 
   $Q^2$, $x_B$,
and t dependencies of the BSA on the bound proton are compared with those on the free proton.
In the whole kinematical region of our measurements, the BSA on the bound proton is smaller by
20\% to 40\%, indicating possible medium modification of its partonic structure.
\end{abstract}
%\pacs{Valid PACS appear here}

@@

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. 
First, events were selected with $Q^2$ greater than $1$ GeV$^2$ and the 
$\gamma^*p$ invariant mass ($W=\sqrt{(q+p)^2}$, assuming that the initial 
nucleon is at rest) greater than $2$ GeV. This is a commonly accepted region of 
kinematics used by the previous DVCS experiments 
%to ensure the applicability of the DVCS handbag diagram and avoid
and avoids the nucleon resonance region. The squared 
transferred momentum to the recoil proton $t$, calculated from the 
four-momentum vectors of the incoming and outgoing photons, was required to be 
greater than a minimum kinematically allowed value ($t_{min}$) at given $Q^2$ 
and $W$ defined as: \begin{equation}
t_{min} 
   =-Q^{2}~\frac{2(1-~x_{B})(1~-~\sqrt{1~+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}},
\end{equation}
where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
proton mass. This cut was applied to avoid accepting events that appear in  
unphysical regions of kinematics due to detector resolution and radiative 
effects.  We specifically use the kinematics of the photons to determine $t$ 
because the initial proton kinematics is unknown due to Fermi motion.
